Object Naming in Language and Vision: A Survey and a New Dataset

### 2019-11-29 papers/LREC2020/lrec2020naming.tex
adressed Carina's comments in abstract

\abstract{
People choose particular names for objects, such as \word{dog} or \word{puppy} for a given dog.
Object naming has been studied in Psycholinguistics, but has received relatively little attention in Computational Linguistics.
We review resources from Language and Vision that could be used to study object naming on a large scale, discuss their shortcomings, and create a new dataset that affords more opportunities for analysis and modeling.
Our dataset, ManyNames, provides 36 name annotations for each of 25K images\cs{objects} selected from VisualGenome.
We highlight the challenges involved and provide a preliminary analysis of the ManyNames data that, on the one hand, shows high consistency in naming, and on the other, suggests that the main source of variation analyzed to date (taxonomic variation, as in \word{chihuahua} vs.\ \word{dog}) may not be the main driver of diversity in naming behavior, \cs{sounds weird:}at least in our setup.\cs{in naming behavior on real-world objects (?)}
% , contrary to expectation, hierarchical variation is not the main source of 
% Massive data collections for applications in language \& vision are nowadays available. In principle, these could constitute valuable resources also for research in computational linguistics (CL). However, in practice, very few studies have tested linguistic hypotheses using these large-scale datasets. In this paper, we illustrate the challenges of using this type of corpora for CL research, by focusing on a case study, namely naming of objects in real-world images. Our analysis of existing resources in language \& vision reveals that available datasets do not generally provide the right type and consistent quality of object naming data,  for being able to conduct a linguistically motivated study of this phenomenon. We contribute a new dataset on top of Visual Genome that  \sz{... continue}
 \\ \newline \Keywords{object naming, language and vision, computer vision} }

>>>>

\abstract{
People choose particular names for objects, such as \word{dog} or \word{puppy} for a given dog.
Object naming has been studied in Psycholinguistics, but has received relatively little attention in Computational Linguistics.
We review resources from Language and Vision that could be used to study object naming on a large scale, discuss their shortcomings, and create a new dataset that affords more opportunities for analysis and modeling.
Our dataset, ManyNames, provides 36 name annotations for each of 25K objects in images selected from VisualGenome.
We highlight the challenges involved and provide a preliminary analysis of the ManyNames data showing that there is a high level of agreement in naming, on average. At the same time, the average number of name types associated with an object is much higher in our dataset than in existing corpora for Language and Vision, such that ManyNames provides a rich resource for studying phenomena like taxonomic variation (\word{chihuahua} vs.\ \word{dog}), which has been discussed a lot in the theoretical literature, and other less well studied phenomena like cross-classification (\word{cake} vs.\ \word{dessert}).
% may not be the main driver of diversity in naming behavior, \cs{sounds weird:}at least in our setup.\cs{in naming behavior on real-world objects (?)}
 \\ \newline \Keywords{object naming, language and vision, computer vision} }
